SST_patterns

### 2019-09-08 SST_patterns.Rmd
fixed_maybe?

# You may then use the 'pixel_match' object to filter out the desired pixels from the full satellite products

match_func <- function(df){
  match <- SACTN_daily_clusters_sub_1  %>% 
  left_join(df, by = c("site", "date")) %>% 
  na.trim()
  return(match)
}

insitu_MUR <- match_func(df = MUR_data)

# OISST_temp <- OISST %>%
#   unite(col = combi, lon, lat, sep = "/", remove = F) %>% 
#   filter(combi %in% pixel_match$combi)

# combined_OISST_match <- CMC %>% 
#   filter(combi %in% pixel_match$combi)

>>>>

# You may then use the 'pixel_match' object to filter out the desired pixels from the full satellite products
temp_match <- function(df){
  temp <- df %>%
  unite(col = combi, lon, lat, sep = "/", remove = F) %>%
  filter(combi %in% pixel_match$combi)
}

OISST_temp <- temp_match(df = OISST)
CMC_temp <- temp_match(df = CMC)
